Information dynamics in neuromorphic nanowire networks

### 2020-06-05 main.tex
change format to SR

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{bbold}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Information dynamics in neuromorphic nanowire networks}% Force line breaks with \\
\thanks{A footnote to the article title}%

\author{Ann Author}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Second Author}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{MUSO Collaboration}%\noaffiliation

\author{Charlie Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Third institution, the second for Charlie Author
}%
\author{Delta Author}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. 
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item. 
\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1}  Introduction}
\section{\label{sec:level1} Method}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{figure/mpl_plot}
	\caption{}
	\label{fig:mpl_plot}
\end{figure}

@@

The non-linear transformation task makes use of sinusoidal wave as the input signal and try to transfer the signal to other periodic signals in the shape of square or sawtooth. Similar to memory capacity test, linear combinations of the network's states are done to fit the target signal. The accuracy is calculated by $1 - \text{RNMSE}$:
\begin{equation}
	\text{RNMSE} = \sqrt{\dfrac{\sum (\mathbf Y - \mathbf O)^2}{\sum \mathbf O^2}}.
\end{equation}
\clearpage

\begin{itemize}
	\item Do we need the current flux vs node centrality? (basically a straight line)
	Nah. Just state node current increases linearly with centrality.
	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
	Probably not - we have more than enough results and I don't think this adds anything.
	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g. the color-way in AIS vs centrality plot.
	Yes, to be consistent and especially if we don't include common. Also, this will combine fig 6 & 7 into one plot, which is better.
	\item How to name different regimes of activation and what will be the time points to distinguish them.
	How about: pre-activation, activation and post-activation?
	\item What will be the best incentive for different initial states in benchmarking. (As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states. This pre-activated way might be a good alternative.)
	Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).
	\item The word usage of node-edge and wire-junction. (In the context of graph/network, seems like node and edge are more understandable. But when talking about ON/OFF and filament states, I feel like junction makes more sense. Should we just use one pair of representation in the paper?)
	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
\end{itemize}

\section{\label{sec:level1} Results}
\subsection{\label{sec:level2} Centrality and Dynamics}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/v_lam_cent}
	\caption{Absolute values of voltage and filament as a function of centrality at T = ?? s. Current path was formed at ??. The data points are colored based on the junctions' corresponding conductance. \textbf{ASK Zdenka. Maybe junction on time will be a more obvious metric.}}
	\label{fig:v_lam_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/I_cent}
	\caption{Current flow on a nanowire vs node centrality}
	\label{fig:i_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/comm_cent}
	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq. \ref{eq:ncomm}. Closeness centrality is calculated by eq. \ref{eq:ecc}. The plot is done on log-log scale. As the nodes at more central positions are having much higher communicabilities (and higher conductance). And the other nodes follows a close to linear trend.}
	\label{fig:comm_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/in_TE}
	\caption{\textbf{Might not need color here. Node in-TE as a function of centrality. (Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted. Each data point represent one junction in one repetition. TE is averaged across the whole time-series. Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$. Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well. All the source-drain pairings are controlled to have same graphical distance. Identical Mackey-Glass signals are applied to these simulations to activate the network. Each data point on the plot represent one node in one simulation. A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.
	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
	\label{fig:in_te}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/TE_cent_act}
	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig. \ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness). Centrality is measured at the current path formation time.}
	\label{fig:TE_cent_act}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/EC_AIS.png}
	\caption{Active information storage of junctions as function of betweenness centrality.}
	\label{fig:EC_AIS}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{figure/time_series}
	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
			\newline (a) Collective conductance of network as a function of time. The collective conductance started increasing when the first junction is turned on. The growth will slow down after the first current path is formed.
			\newline (b) The time derivative of conductance. The derivative is calculated using second order accurate central differences on the collective conductance time series data. The growth regime of conductance shows a great correspondence of $\Delta G$'s spikes.
			\newline (c) Transfer entropy as a function of time. The transfer entropy time series data here is calculated with the Kraskov estimator and averaged across the network. A moving average with window size of 100 is applied to smooth the curve. Transfer entropy in the activation period is significantly higher than the rest.
			\newline (d) Modularity as a function of time. The weighted modularity of network is calculated by Louvain method(Eq. \ref{eq:mod}) As the network evolves, modularity will first increase as high conductance junctions are spread across the network and having their own communities. With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected. Then the modularity will keep having such fluctuations with smaller scales as more junctions are turned on and forming new current paths.
			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
	\label{fig:time_series}
\end{figure}

\begin{figure}[]
	\centering
	\includegraphics[width=1\linewidth]{figure/time_align}
	\caption{\textbf{Key events time as functions of first current path formation time.} 
			The same 100 network is used for 50 simulations with different source-drain pairings. The graphical distances between sources and drains are controlled to be constant. Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations. Simulations with higher amplitudes will form current paths earlier. 
			\newline 
			X-axis represents the current path formation time in different simulations. Y-axis represents the corresponding time for key events to take place in these simulations. As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time. 
			\newline
			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on. }
	\label{fig:time_align}
\end{figure}

\clearpage
\section{\label{sec:level1} Discussion}

\section{\label{sec:level1} Conclusion}

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\appendix

\section{Appendixes}

\section{A little more on appendixes}

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
\nocite{*}

\bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

>>>>

\documentclass[fleqn,10pt,  amsmath,amssymb,aps]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{cleveref}

\title{Information dynamics in neuromorphic nanowire networks}

\author[1,*]{Alice Author}
\author[2]{Bob Author}
\author[1,2,+]{Christine Author}
\author[2,+]{Derek Author}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{corresponding.author@email.example}

\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The Introduction section, of referenced text expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

%\begin{itemize}
%	\item Do we need the current flux vs node centrality? (basically a straight line)
%	Nah. Just state node current increases linearly with centrality.
%	\item Do we need communicability? Since COMM = $\sum G^k$ in my definition.
%	Probably not - we have more than enough results and I don't think this adds anything.
%	\item  For the coloring of TE scatter, ON time might be a more straight forward scheme, e.g. the color-way in AIS vs centrality plot. [Yes, to be consistent and especially if we don't include common. Also, this will combine fig 6 & 7 into one plot, which is better.]
%	\item How to name different regimes of activation and what will be the time points to distinguish them.
%	How about: pre-activation, activation and post-activation?
%	\item What will be the best incentive for different initial states in benchmarking. (As far as I know, most of the reservoir computing realizations are based on homogeneous or randomly generated initial states. This pre-activated way might be a good alternative.)[Let's ask Joe - he and Mac & Mike were looking into this with ANNs as there is now some literature on pre-activating ANNs (but not ESNs/RC networks ).]
%	\item The word usage of node-edge and wire-junction. (In the context of graph/network, seems like node and edge are more understandable. But when talking about ON/OFF and filament states, I feel like junction makes more sense. Should we just use one pair of representation in the paper?)
%	 Yes we should try and be consistent. For this study, we don't need to use filament, but I think we can interchangably use node/wire and edge/junction, and junction state.
%\end{itemize}

\clearpage
\section*{Results}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/v_lam_cent}
	\caption{Absolute values of voltage and filament as a function of centrality at T = ?? s. Current path was formed at ??. The data points are colored based on the junctions' corresponding conductance. \textbf{ASK Zdenka. Maybe junction on time will be a more obvious metric.}}
	\label{fig:v_lam_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/I_cent}
	\caption{Current flow on a nanowire vs node centrality}
	\label{fig:i_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/comm_cent}
	\caption{\textbf{Node communicability vs closeness centrality at $t = 2 s$.} Node communicability is calculated by eq. \ref{eq:ncomm}. Closeness centrality is calculated by eq. \ref{eq:ecc}. The plot is done on log-log scale. As the nodes at more central positions are having much higher communicabilities (and higher conductance). And the other nodes follows a close to linear trend.}
	\label{fig:comm_cent}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/in_TE}
	\caption{\textbf{Might not need color here. Node in-TE as a function of centrality. (Out TE in  supplement)} 50 repetitions with different source-drain pairings on the same 100 nw network are plotted. Each data point represent one junction in one repetition. TE is averaged across the whole time-series. Node centrality is calculated based on the current-flow closeness algorithm at $t = 0$. Communicability is calculated by Eq \textbf{equation} at $t = 0$ as well. All the source-drain pairings are controlled to have same graphical distance. Identical Mackey-Glass signals are applied to these simulations to activate the network. Each data point on the plot represent one node in one simulation. A close to linear correlation between TE and centrality can be determined from the plot, which means nodes with higher centralities tend to have richer dynamics for taking in and sending out information.
	\textbf{Intrinsic property of the network that does not have any dynamics. We have structural information here.}}
	\label{fig:in_te}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/TE_cent_act}
	\caption{\textbf{In-TE vs closeness centrality around activation.} The same activation test is done as fig. \ref{fig:in_te}.	TE is averaged in a $0.2s$ window right before the activation (mainly to cancel out the randomness). Centrality is measured at the current path formation time.}
	\label{fig:TE_cent_act}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/EC_AIS.png}
	\caption{Active information storage of junctions as function of betweenness centrality.}
	\label{fig:EC_AIS}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{figure/time_series}
	\caption{\textbf{Time series data for network measures.} The dashed vertical green line represents the 			time of first current path formation.
			\newline (a) Collective conductance of network as a function of time. The collective conductance started increasing when the first junction is turned on. The growth will slow down after the first current path is formed.
			\newline (b) The time derivative of conductance. The derivative is calculated using second order accurate central differences on the collective conductance time series data. The growth regime of conductance shows a great correspondence of $\Delta G$'s spikes.
			\newline (c) Transfer entropy as a function of time. The transfer entropy time series data here is calculated with the Kraskov estimator and averaged across the network. A moving average with window size of 100 is applied to smooth the curve. Transfer entropy in the activation period is significantly higher than the rest.
			\newline (d) Modularity as a function of time. The weighted modularity of network is calculated by Louvain method(Eq. \ref{eq:mod}) As the network evolves, modularity will first increase as high conductance junctions are spread across the network and having their own communities. With the formation of the first current path, the modularity will have a significant drop since these isolating communities are connected. Then the modularity will keep having such fluctuations with smaller scales as more junctions are turned on and forming new current paths.
			\textbf{Gaussian -linear inter, KSG - nonlinear, sensitive}}
	\label{fig:time_series}
\end{figure}

\begin{figure}[]
	\centering
	\includegraphics[width=0.5\linewidth]{figure/time_align}
	\caption{\textbf{Key events time as functions of first current path formation time.} 
			The same 100 network is used for 50 simulations with different source-drain pairings. The graphical distances between sources and drains are controlled to be constant. Identical Mackey-Glass signal with random amplitudes ranging between 2-5 V are applied to these simulations. Simulations with higher amplitudes will form current paths earlier. 
			\newline 
			X-axis represents the current path formation time in different simulations. Y-axis represents the corresponding time for key events to take place in these simulations. As shown in this figure, key events such as $\Delta G$ maximum, TE spike (in Gaussian estimation) and modularity drop will happen around the first current path formation time. 
			\newline
			\textbf{Rephrase here} Thus the network will be optimal for information processing and specific task around the transition phase when the first current path is forming and the network is turning on. }
	\label{fig:time_align}
\end{figure}

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\linewidth]{figure/mpl_plot}
	\caption{}
	\label{fig:mpl_plot}
\end{figure}

@@

The non-linear transformation task makes use of sinusoidal wave as the input signal and try to transfer the signal to other periodic signals in the shape of square or sawtooth. Similar to memory capacity test, linear combinations of the network's states are done to fit the target signal. The accuracy is calculated by $1 - \text{RNMSE}$:
\begin{equation}
	\text{RNMSE} = \sqrt{\dfrac{\sum (\mathbf Y - \mathbf O)^2}{\sum \mathbf O^2}}.
\end{equation}

\bibliography{paper1}\label{paper1}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Hao:gidmaps:2014}.

For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}
